Reference Tracking Strategies of Native and Late Signers in Turkish Sign Language

### 2022-08-06 revised_manuscript.Rmd
updated files

---
editor_options:
  chunk_output_type: console
title: Reference Tracking Strategies of Native and Late Signers in Turkish Sign Language
abstract: |
  We investigated the reference tracking strategies among native and late adult deaf signers of Turkish Sign Language. Consistent with the theories of saliency and referential accessibility, regardless of their acquisiton groups, signers mainly used nominals and extension classifiers for introducing referents. To maintain a referent in the previous clause, signers chose null marking (e.g., constructed action, agreement and plain verbs). For topic shifts or re-introduced contexts, nominals and pronouns were chiefly favored although we observed very little pronominal use. As for age of acquisition effects, we only report limited over-redundancy for late signers who used null marking less compared to native signers especially for introduced and maintained contexts. Given our limited support for redundancy by late signers, we conclude that native signers might utilize the spatial affordances of the visual-spatial modality better than late signers only to a certain extent.
keywords: "Referential accessibility, signed narratives, pragmatic competence, delayed language acquisition, Turkish Sign Language"
journal: "Journal of Pragmatics"
date: "`r Sys.Date()`"
bibliography: ./bibliography/references.bib
times: true
numbersections: true
classoption: "review"
csl: ./bibliography/elsevier-harvard.csl
output: rticles::elsevier_article
header-includes:
   - \usepackage{floatrow}
   - \usepackage{hyperref}
   - \usepackage{enumitem}  
   - \usepackage{float}
   - \floatplacement{figure}{H}
   - \floatplacement{table}{H}
   - \floatsetup[figure]{capposition=top}
   - \floatsetup[table]{capposition=top}
   - \usepackage{times}
   - \usepackage{smartdiagram}
   - \usepackage{ragged2e}
   - \usepackage{tikz}
   - \usepackage{xcolor}
   - \usepackage[utf8]{inputenc}
   - \usepackage[T1]{fontenc}
   - \usepackage{graphicx}
   - \usepackage{./sty/langsci-gb4e}
   - \usepackage{caption}
   - \usepackage{multicol}
   - \setlength{\columnsep}{-3cm}
   - \usepackage{setspace}
---

@@

Sign Languages are natural languages of the Deaf communities all around the world. They are independent languages, which do not derive from majority spoken language(s) but emerge naturally when deaf people form a community. Turkish Sign Language (Türk İşaret Dili -- TİD) is and has been the officially recognized language of the Deaf community in Turkey since 2005 [see @nuhbalaoglu2018 for a brief review of the historical development of the language]. Deaf or hearing children acquiring a SL within a family where there is one or more deaf caregivers display the same developmental milestones as hearing children acquiring a spoken language in a hearing family [@chamberlain_language_1999; @meier1990]. However, reports indicate that over 90% of all deaf individuals are born into hearing families who do not know how to sign (i.e., those with language deprivation) [@woll2013]. This means that the auditory modality used in the household is not accessible to many deaf children. That is why the age of acquisition of a first functional language varies greatly among deaf children, with many of whom being deprived of their first languages typically until after age 7 when they start formal education in a deaf school. First language deprivation or delay has been found to have negative effects on certain cognitive and linguistic measures among late signing children. To name a few, delayed exposure to a first functional language is reported to negatively affect deaf children and adults' morphosyntactic production and processing [@kayabasi2020; @boudreault2006; @newport1990; @cheng2021; @karadoller2017; @cormier2012] and narrative abilities [e.g., @becker2009]. In our overall research, we are concerned with the effects of this late exposure in the ultimate adult forms of TİD users.

@@

However, this particular observation is not peculiar to spoken languages. There is an emerging body of literature that reports the distribution of REs in signed narratives. Building on @gundel1993's work, @swabey2002 demonstrated that, like other spoken languages such as Russian, Chinese, and Japanese, American Sign Language (ASL) signers use bare nouns for introduced and re-introduced discourse contexts whereas null marking is used for referents which are "in-focus" or very accessible to the addressee. Overt REs like pronouns or nouns are disprefered for such referents. @swabey2002 concluded that "native" signers in her study abided by the Gricean maxim of quantity and were thus economic in their reference tracking. Similar findings have been reported for German Sign Language (Deutsche Gebärdensprache - DGS) [@perniss2015] and British Sign Language (BSL) [@morgan2005]. It is important to note, however, that these research either collapsed native and late signers into a single group and labeled them as "native-like" or explicitly compared native deaf signers with late deaf signers (with language deprivation) in terms of narrative competence.

### Signed vs. Spoken REs

Commonly in both spoken and sign languages nouns and noun phrases are used as REs. Spoken languages use pronouns, determines and demonstratives where sign languages use a pointing sign, usually glossed as IX, which assumes similar functions [@lillo-martin1990]. In addition, the pointing sign is used to referentially anchor a referent to a location in signing space. For instance, when the signer introduces \textsc{elvan} for the first time, s/he can assign her to the right. This referential locus can later be used by agreement verbs and classifier predicates (more below). For instance, in (\ref{ex:2a}) there are two referents, \textsc{elvan}, who is referentially-assigned to the right side of the signer, represented with the "A" subscript and \textsc{demet}, who is referentially-assigned to the left side of the signer, represented with the "B" subscript. When the signer makes a contrast in (\ref{ex:2b}), as a pronominal use, she points to the right side to refer to ELVAN and to the left to refer to \textsc{demet}. We schematically represent the referential locus assigned to the referents in (\ref{ex:3}).

@@

% Text Node
\draw (88.75,80.75) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\footnotesize Locus-b }};
% Text Node
\draw (91.75,90.25) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny (Demet)}};
% Text Node
\draw (208.25,80.75) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\footnotesize Locus-a }};
% Text Node
\draw (212.75,90.25) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny (Elvan)}};
% Text Node
\draw (144,115.25) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\footnotesize Signer}};
\end{tikzpicture}
    \end{exe}
```
Grammatical gender as in Romance languages or noun classes as in Bantu languages are some reference tracking tools that are familiar from spoken languages. A somehow less known reference-tracking tool in spoken languages is *verbal classifiers*, which morphologically attach to the verb and often cross-reference a core argument in a clause [@aikhenvald2017]. Classifiers denote sets of objects based on semantic criteria such as size, shape, body-part, texture and sometimes function. Usually, the verbal classifier and the cross-referenced noun co-occur in the same clause when the argument is introduced into discourse. The classifier can track the argument on its own on subsequent occurrences. In sign languages, a verbal classifier morpheme is encoded by a *handshape* that is articulated phonologically co-temporally with a movement, which encodes the verbal meaning [@supalla1990; @benedicto2004]. These two infused morphemes form a complex predicate. Some classifier handshapes and the set of objects that they denote are presented below in (\ref{ex:4}).

@@

    \ex \textsc{tree} assigned to the referential locus-b. The source and goal tracked on the predicates \textsc{fly} and \textsc{land}. \\ \\
    \textsc{bird fly[manner]-a tree-b land cl-b}\\
    ‘The bird flies (from the cage assigned to the left) to a tree (assigned to the right).’
    \end{xlist}
    \end{exe}
    \hfill (Adapted from Gökgöz and Sevgi 2020:318)
```
## Linguistic Tools for Tracking Referents in Signed Narratives

```{=tex}
\begin{multicols}{2}
\begin{exe}
\ex
\begin{xlist}
\ex \label{ex:6a} Full noun \\\glll
\includegraphics[width=50pt]{pictures/1a_1.png}\\ \textsc{mouse\footnotemark} \\ \\ 
\ex \label{ex:6b} Noun modified by classifier \\\glll
\includegraphics[width=50pt]{pictures/1c_2.png} \includegraphics[width=50pt]{pictures/1c_1.png} \\ \textsc{soap} \textsc{soap.cl} \\ \\ 
\ex \label{ex:6c} Fingerspelled noun\\\glll 
\includegraphics[width=50pt]{pictures/1b_1.png} \includegraphics[width=50pt]{pictures/1b_2.png} \includegraphics[width=50pt]{pictures/1b_3.png}\\ \textsc{t-} \textsc{o-} \textsc{m} \\ \\
\ex \label{ex:6d} Noun modified by index (\textsc{IX})\\\glll 
\includegraphics[width=50pt]{pictures/1d_1.png} \includegraphics[width=50pt]{pictures/1d_2.png}\\ \textsc{ix} \textsc{cat} \\ \\
\end{xlist}
\end{exe}
\end{multicols}
\ea 
\ea \label{ex:7} Pronominal \\\glll
\includegraphics[width=50pt]{pictures/2_1.png} \includegraphics[width=50pt]{pictures/2_2.png} \\ \textsc{ix} \textsc{sick} \\ \\
\z \z
\begin{multicols}{4}
\begin{exe}
\ex \label{ex:8}
\begin{xlist}
\ex Whole entity \\\glll 
\includegraphics[width=50pt]{pictures/3e.png} \\ \textsc{fish.fall}\\ \\
\ex Body part \\\glll
\includegraphics[width=50pt]{pictures/3b.png} \\ \textsc{walk} \\ \\ 
\ex Handling \\\glll 
\includegraphics[width=50pt]{pictures/3c.png} \\ \textsc{hold} \\ \\
\ex Extension \\\glll 
\includegraphics[width=50pt]{pictures/3d_1.png} \includegraphics[width=50pt]{pictures/3a.png}\\ \textsc{plank} {\textsc{dh: mouse}} \\ {} {\textsc{ndh: tunnel}}\\ \\
\end{xlist}
\end{exe}
\end{multicols}
\begin{multicols}{3}
\begin{exe}
\ex
\begin{xlist}
\ex \label{ex:9a} Constructed action \\\glll 
\includegraphics[width=50pt]{pictures/4c.png} \\ \textsc{struggle} \\ \\

\ex \label{ex:9c} Agreement verb  \\\glll 
\includegraphics[width=50pt]{pictures/4b_1.png} 
\includegraphics[width=50pt]{pictures/4b_2.png} \\ {\textsc{$_{1}$hit$_{3}$}} {} \\ \\ 
\end{xlist}
\end{exe}
\end{multicols}
\footnotetext{We use small capitals to indicate sign glosses.}
```
### Nominals

The IX sign (extended index finger) has various functions in sign languages, one of which is the pronominal use which refers to established nominals by pointing to a previously assigned abstract or physical locus in the signing space when re-introducing a topic in discourse [@emmorey1996]. The same IX function has also been identified for TİD [@sevinc2006]. The example in (\ref{ex:7}) illustrates a spatially-anchored pronominal reference for topic re-introduction. These signs are thus rarely used for the first mention of an entity [@perniss2015]. Other interpretations consider pointing signs without noun phrases as examples of demonstratives and not personal pronouns [@koulidobrova2016]. It is important to mention here that in some spoken languages (e.g., German and Dutch), demonstratives can also refer to persons [@bosch2007] and behave similarly to personal pronouns. However, for the purposes of the present study, we will refer to IX constructions as pronominal IX and particularly examine their non-deictic or personal pronoun realizations as a possible discourse strategy to mainly mark topic shift among native and late signers of TİD.

Classifier predicates are highly complex morphological constructions which are very common in sign languages [@supalla1986]. These are manually signed iconic representations of animate or inanimate objects, and they embody several properties pertaining to the nominal referent including its location in the signing space, movement, path, size, and shape [@talmy2003]. As in most sign languages hitherto studied, classifier constructions are also commonly found in TİD [see @dikyuva2015 for a review]. Following the classification of @engberg-pedersen1993, we distinguish between four types of classifier constructions. Whole entity classifiers (WECL) represent the entirety of any referent whereas body part classifiers (BPCL) only reflect a specific part of an animate entity (e.g., limbs, head, tongue, teeth, and so forth). Handling classifiers (HCL) occur with transitive verbs and depict how an object is handled or manipulated by an agent. On this ground, an HCL[^1] depicts the manner of the referring action while the former two constructions encode the location of the entity as well as its motion in space. Extension classifiers (ExtCL), on the other hand, denote the size and shape of an entity by following a trajectory to trace its shape. We exemplify these constructions in (\ref{ex:8}).

### Null marking

## Learning How to Track Referents in Sign Languages

>>>>

---
editor_options:
  chunk_output_type: console
title: Reference Tracking Strategies of Native and Late Signers in Turkish Sign Language
abstract: |
  We investigated the reference tracking strategies among native and late adult deaf signers of Turkish Sign Language. Consistent with the theories of saliency and referential accessibility, regardless of their acquisiton groups, signers mainly used nominals and extension classifiers for introducing referents. To maintain a referent in the previous clause, signers chose null marking (e.g., constructed action, agreement and plain verbs). For topic shifts or re-introduced contexts, nominals and pronouns were chiefly favored although we observed very little pronominal use. As for age of acquisition effects, we only report limited over-redundancy for late signers who used null marking less compared to native signers especially for introduced and maintained contexts. Given our limited support for redundancy by late signers, we conclude that native signers might utilize the spatial affordances of the visual-spatial modality better than late signers only to a certain extent.
keywords: "Referential accessibility, signed narratives, pragmatic competence, delayed language acquisition, Turkish Sign Language"
journal: "Journal of Pragmatics"
date: "`r Sys.Date()`"
bibliography: ./bibliography/references.bib
times: true
numbersections: trueand w
classoption: "review"
csl: ./bibliography/elsevier-harvard.csl
output: rticles::elsevier_article
header-includes:
   - \usepackage{floatrow}
   - \usepackage{hyperref}
   - \usepackage{enumitem}  
   - \usepackage{float}
   - \floatplacement{figure}{H}
   - \floatplacement{table}{H}
   - \floatsetup[figure]{capposition=top}
   - \floatsetup[table]{capposition=top}
   - \usepackage{times}
   - \usepackage{smartdiagram}
   - \usepackage{ragged2e}
   - \usepackage{tikz}
   - \usepackage{xcolor}
   - \usepackage[utf8]{inputenc}
   - \usepackage[T1]{fontenc}
   - \usepackage{graphicx}
   - \usepackage{./sty/langsci-gb4e}
   - \usepackage{caption}
   - \usepackage{multicol}
   - \setlength{\columnsep}{-3cm}
   - \usepackage{setspace}
---

@@

Sign Languages are natural languages of the Deaf communities all around the world. They are independent languages, which do not derive from majority spoken language(s) but emerge naturally when deaf people form a community. Turkish Sign Language (Türk İşaret Dili -- TİD) is and has been the officially recognized language of the Deaf community in Turkey since 2005 [see @nuhbalaoglu2018 for a brief review of the historical development of the language]. Deaf or hearing children acquiring a SL within a family where there is one or more deaf caregivers display the same developmental milestones as hearing children acquiring a spoken language in a hearing family [@chamberlain_language_1999; @meier1990]. However, reports indicate that over 90% of all deaf individuals are born into hearing families who do not know how to sign (i.e., those with language deprivation) [@woll2013]. This means that the auditory modality used in the household is not accessible to many deaf children. That is why the age of acquisition of a first functional language varies greatly among deaf children, with many of whom being deprived of their first languages typically until after age 7 when they start formal education in a deaf school. Despite this, many of the early intervention programs for late signing children prioritize spoken language development and discourage the use of a sign language [@kemaloglu2012]. @ministryofnationaleducation2020 identifies 72 deaf schools in Turkey for the K-12 level. Even when deaf children with hearing parents start their formal education in one of these schools, they do not receive proper instruction in TİD since the teachers themselves are mainly hearing and only have a very rudimentary knowledge of a sign language [@ilkbasaran2015]. First language deprivation or delay has been found to have negative effects on certain cognitive and linguistic measures among late signing children. To name a few, delayed exposure to a first functional language is reported to negatively affect deaf children and adults' morphosyntactic production and processing [@kayabasi2020; @boudreault2006; @newport1990; @cheng2021; @karadoller2017; @cormier2012] and narrative abilities [e.g., @becker2009]. In our overall research, we are concerned with the effects of this late exposure in the ultimate adult forms of TİD users.

@@

However, this particular observation is not peculiar to spoken languages. There is an emerging body of literature that reports the distribution of REs in signed narratives [@czubek2017; @swabey2002; @frederiksen2016; @perniss2015; @morgan2005; @hodge2019; @ahlgren1994]. Building on @gundel1993's work, @swabey2002 demonstrated that, like other spoken languages such as Russian, Chinese, and Japanese, American Sign Language (ASL) signers use bare nouns for introduced and re-introduced discourse contexts whereas null marking is used for referents which are "in-focus" or very accessible to the addressee. Overt REs like pronouns or nouns are disprefered for such referents. @swabey2002 concluded that "native" signers in her study abided by the Gricean maxim of quantity and were thus economic in their reference tracking. Similar findings have been reported for German Sign Language (Deutsche Gebärdensprache - DGS) [@perniss2015] and British Sign Language (BSL) [@morgan2005]. It is important to note, however, that these research either collapsed native and late signers into a single group and labeled them as "native-like" or explicitly compared native deaf signers with late deaf signers (with language deprivation) in terms of narrative competence.

## Linguistic Tools for Tracking Referents in Signed Narratives

### Nominals

The IX sign (extended index finger) has various functions in sign languages, one of which is the pronominal use which refers to established nominals by pointing to a previously assigned abstract or physical locus in the signing space when re-introducing a topic in discourse [@emmorey1996]. The same IX function has also been identified for TİD [@sevinc2006]. The example in (\ref{ex:7}) illustrates a spatially-anchored pronominal reference for topic re-introduction. These signs are thus rarely used for the first mention of an entity [@perniss2015]. Other interpretations consider pointing signs without noun phrases as examples of demonstratives and not personal pronouns [@koulidobrova2016]. However, for the purposes of the present study, we will refer to IX constructions as pronominal IX and particularly examine their non-deictic or personal pronoun realizations as a possible discourse strategy to mainly mark topic shift among native and late signers of TİD.

Classifier predicates are highly complex morphological constructions which are very common in sign languages [@supalla1986]. These are manually signed iconic representations of animate or inanimate objects, and they embody several properties pertaining to the nominal referent including its location in the signing space, movement, path, size, and shape [@talmy2003]. As in most sign languages hitherto studied, classifier constructions are also commonly found in TİD [see @dikyuva2015 for a review]. Following the classification of @engberg-pedersen1993, we distinguish between four types of classifier constructions. Whole entity classifiers (WECL) represent the entirety of any referent whereas body part classifiers (BPCL) only reflect a specific part of an animate entity (e.g., limbs, head, tongue, teeth, and so forth). Handling classifiers (HCL[^1]) occur with transitive verbs and depict how an object is handled or manipulated by an agent. Extension classifiers (ExtCL), on the other hand, denote the size and shape of an entity by following a trajectory to trace its shape. We exemplify these constructions in (\ref{ex:8}).

```{=tex}
\begin{multicols}{2}
\begin{exe}
\ex
\begin{xlist}
\ex \label{ex:6a} Full noun \\\glll
\includegraphics[width=50pt]{pictures/1a_1.png}\\ \textsc{mouse\footnotemark} \\ \\ 
\ex \label{ex:6b} Noun modified by classifier \\\glll
\includegraphics[width=50pt]{pictures/1c_2.png} \includegraphics[width=50pt]{pictures/1c_1.png} \\ \textsc{soap} \textsc{soap.cl} \\ \\ 
\ex \label{ex:6c} Fingerspelled noun\\\glll 
\includegraphics[width=50pt]{pictures/1b_1.png} \includegraphics[width=50pt]{pictures/1b_2.png} \includegraphics[width=50pt]{pictures/1b_3.png}\\ \textsc{t-} \textsc{o-} \textsc{m} \\ \\
\ex \label{ex:6d} Noun modified by index (\textsc{IX})\\\glll 
\includegraphics[width=50pt]{pictures/1d_1.png} \includegraphics[width=50pt]{pictures/1d_2.png}\\ \textsc{ix} \textsc{cat} \\ \\
\end{xlist}
\end{exe}
\end{multicols}
\ea 
\ea \label{ex:7} Pronominal \\\glll
\includegraphics[width=50pt]{pictures/2_1.png} \includegraphics[width=50pt]{pictures/2_2.png} \\ \textsc{ix} \textsc{sick} \\ \\
\z \z
\clearpage
\begin{multicols}{4}
\begin{exe}
\ex \label{ex:8}
\begin{xlist}
\ex Whole entity \\\glll 
\includegraphics[width=50pt]{pictures/3e.png} \\ \textsc{fish.fall}\\ \\
\ex Body part \\\glll
\includegraphics[width=50pt]{pictures/3b.png} \\ \textsc{walk} \\ \\ 
\ex Handling \\\glll 
\includegraphics[width=50pt]{pictures/3c.png} \\ \textsc{hold} \\ \\
\ex Extension \\\glll 
\includegraphics[width=50pt]{pictures/3d_1.png} \includegraphics[width=50pt]{pictures/3a.png}\\ \textsc{plank} {\textsc{dh: mouse}} \\ {} {\textsc{ndh: tunnel}}\\ \\
\end{xlist}
\end{exe}
\end{multicols}
\begin{multicols}{3}
\begin{exe}
\ex
\begin{xlist}
\ex \label{ex:9a} Constructed action \\\glll 
\includegraphics[width=50pt]{pictures/4c.png} \\ \textsc{struggle} \\ \\

\ex \label{ex:9c} Agreement verb  \\\glll 
\includegraphics[width=50pt]{pictures/4b_1.png} 
\includegraphics[width=50pt]{pictures/4b_2.png} \\ {\textsc{$_{1}$hit$_{3}$}} {} \\ \\ 
\end{xlist}
\end{exe}
\end{multicols}
\footnotetext{We use small capitals to indicate sign glosses.}
```
### Null marking

## Signed vs. Spoken REs

Commonly in both spoken and sign languages nouns and noun phrases are used as REs. Spoken languages use pronouns, determines and demonstratives where sign languages use a pointing sign, usually glossed as IX, which assumes similar functions [@lillo-martin1990]. It is important to mention here that in some spoken languages (e.g., German and Dutch), demonstratives can also refer to persons [@bosch2007] and behave similarly to personal pronouns. In addition, the pointing sign is used to referentially anchor a referent to a location in signing space. For instance, when the signer introduces \textsc{elvan} for the first time, s/he can assign her to the right. This referential locus can later be used by agreement verbs and classifier predicates (more below). For instance, in (\ref{ex:2a}) there are two referents, \textsc{elvan}, who is referentially-assigned to the right side of the signer, represented with the "A" subscript and \textsc{demet}, who is referentially-assigned to the left side of the signer, represented with the "B" subscript. When the signer makes a contrast in (\ref{ex:2b}), as a pronominal use, she points to the right side to refer to ELVAN and to the left to refer to \textsc{demet}. We schematically represent the referential locus assigned to the referents in (\ref{ex:3}).

@@

% Text Node
\draw (88.75,80.75) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\footnotesize Locus-b }};
% Text Node
\draw (91.75,90.25) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny (Demet)}};
% Text Node
\draw (208.25,80.75) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\footnotesize Locus-a }};
% Text Node
\draw (212.75,90.25) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny (Elvan)}};
% Text Node
\draw (144,115.25) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\footnotesize Signer}};
\end{tikzpicture}
    \end{exe}
```
Grammatical gender as in Romance languages or noun classes as in Bantu languages are some reference tracking tools that are familiar from spoken languages. A somehow less known reference-tracking tool in spoken languages is *verbal classifiers*, which morphologically attach to the verb and often cross-reference a core argument in a clause [@aikhenvald2017]. As outlined in the previous section, classifiers denote sets of objects based on semantic criteria such as size, shape, body-part, texture and sometimes function. Usually, the verbal classifier and the cross-referenced noun co-occur in the same clause when the argument is introduced into discourse. The classifier can track the argument on its own on subsequent occurrences. In sign languages, a verbal classifier morpheme is encoded by a *handshape* that is articulated phonologically co-temporally with a movement, which encodes the verbal meaning [@supalla1990; @benedicto2004]. These two infused morphemes form a complex predicate. Some classifier handshapes and the set of objects that they denote are presented below in (\ref{ex:4}).

@@

    \ex \textsc{tree} assigned to the referential locus-b. The source and goal tracked on the predicates \textsc{fly} and \textsc{land}. \\ \\
    \textsc{bird fly[manner]-a tree-b land cl-b}\\
    ‘The bird flies (from the cage assigned to the left) to a tree (assigned to the right).’
    \end{xlist}
    \end{exe}
    \hfill (Adapted from Gökgöz and Sevgi 2020:318)
```
## Learning How to Track Referents in Sign Languages
